# Base R

## R Syntax & Data Types

### Slides

```{r embed-xaringan-1, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#18", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #18)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#18)

### Video

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=S8zTmEvpYYk")
```

### Exercise 1

1. Do the following calculation in R: one plus five, divided by nine.

2. Assign the result of the calculation to a variable.

3. Test if the result of your calculation is larger than 1.

4. Round off the result to 1 decimal. Tip: use the Maths Functions section of the Base R cheat sheet!

### Solution

#### Slides {-}

```{r embed-xaringan-2, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#27", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #27)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#27)

#### Video {-}

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=V8za6GR7u8Q&feature=youtu.be")
```

## Vectors in R

### Slides

```{r embed-xaringan-3, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#28", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #28)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#28)

### Video

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=XMFjteCdHbQ")
```

### Exercise 2

Meet Ann, Bob, Chloe, and Dan.

1. Make a character vector with their names, using the function c(). Save the vector as "name".

2. How old are Ann, Bob, Chloe, and Dan? You decide! Design a numeric vector with their respective ages. Save it as "age".

3. What is their average age? Use a function in R to calculate this. Tip: use the Maths Functions section of the Base R cheat sheet!

### Solution

#### Slides {-}


```{r embed-xaringan-4, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#40", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #40)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#40)

#### Video {-}

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=rIieuoYT4z0")
```

## Data Structures

### Slides

```{r embed-xaringan-5, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#41", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #41)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#41)

### Video

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=Ffk2Kxa_b_M")
```

### Exercise 3

1. Create a vector country containing four countries (use at least one duplicate!).

2. Create a data frame combining name, age, and country, and save it as df.

3. Check your dataframe with the function summary(). Does it contain a factor?

4. Make sure your column country is a factor, and confirm this with summary().

5. Create a list with your vectors name and age, and save it as mylist.

### Solution

#### Slides {-}

```{r embed-xaringan-6, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#50", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #50)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#50)

#### Video {-}

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=A1GsHC6pIio")
```

## Missing Data

### Slides

```{r embed-xaringan-7, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#53", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #53)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#53)

### Video

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=4gVvlg1Itzs")
```

### Exercise 4

Predict the results before you run the code. Does the real answer make sense to you?

### Solution

#### Slides {-}

```{r embed-xaringan-8, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#63", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #63)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#63)

## Indexing Vectors & Lists

### Slides
```{r embed-xaringan-9, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#66", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #66)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#66)

### Video

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=e10nO2swYIE")
```

### Exercise 5

1. Return only the first number in your vector age.

2. Return the 2nd and 4th name in your vector name.

3. Return only ages under 30 from your vector age.

4. Return the name "Chloe" from your list mylist (see exercise 3).

### Solution

#### Slides {-}

```{r embed-xaringan-10, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#79", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #79)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#79)

#### Video {-}

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=4BZGGq-nBos")
```

## Indexing a Data Frame

### Slides

```{r embed-xaringan-11, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#80", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #80)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#80)

### Video

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=m15hbXG6I-Y")
```

### Exercise 6

1. From your dataframe df, return the entries for everyone living in a country of your choice.

2. Return only the names of everyone in your data frame df under 40. 
   (Hint: what information should you use for row indexing? 
	 What information should you use for column indexing?)
	 
3. Return the columns name and age together.

### Solution

#### Slides {-}

```{r embed-xaringan-12, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#91", ratio = "4:3")
```

[Use this link to open slides in a new tab (refer to slide #91)](https://utrechtuniversity.github.io/workshop-introduction-to-R-and-data/slides/slides_introduction.html#91)

#### Video {-}

```{r echo=FALSE}
vembedr::embed_url("https://www.youtube.com/watch?v=DUk9bfcSwbA")
```
